\thusetup{
  %******************************
  % 注意：
  %   1. 配置里面不要出现空行
  %   2. 不需要的配置信息可以删除
  %******************************
  %
  %=====
  % 秘级
  %=====
  secretlevel={秘密},
  secretyear={10},
  %
  %=========
  % 中文信息
  %=========
  ctitle={基于GPU的极化SAR图像舰船检测算法设计},
  cdegree={工学硕士},
  cdepartment={电子工程系},
  cmajor={电子信息科学与技术},
  cauthor={孙天宇},
  csupervisor={杨健\ 教授},
   % 日期自动使用当前时间，若需指定按如下方式修改：
  cdate={2020年5月15日},
  %
  %=========
  % 英文信息
  %=========
  etitle={An Introduction to \LaTeX{} Thesis Template of Tsinghua University v\version},
  % 这块比较复杂，需要分情况讨论：
  % 1. 学术型硕士
  %    edegree：必须为Master of Arts或Master of Science（注意大小写）
  %             “哲学、文学、历史学、法学、教育学、艺术学门类，公共管理学科
  %              填写Master of Arts，其它填写Master of Science”
  %    emajor：“获得一级学科授权的学科填写一级学科名称，其它填写二级学科名称”
  % 2. 专业型硕士
  %    edegree：“填写专业学位英文名称全称”
  %    emajor：“工程硕士填写工程领域，其它专业学位不填写此项”
  % 3. 学术型博士
  %    edegree：Doctor of Philosophy（注意大小写）
  %    emajor：“获得一级学科授权的学科填写一级学科名称，其它填写二级学科名称”
  % 4. 专业型博士
  %    edegree：“填写专业学位英文名称全称”
  %    emajor：不填写此项
  edegree={Doctor of Engineering},
  emajor={Computer Science and Technology},
  eauthor={Xue Ruini},
  esupervisor={Professor Zheng Weimin},
  eassosupervisor={Chen Wenguang},
  % 日期自动生成，若需指定按如下方式修改：
  % edate={December, 2005}
  %
  % 关键词用“英文逗号”分割
  ckeywords={舰船检测, 高性能计算, 极化白化滤波器, 极化协方差差异矩阵, 极化SAR},
  ekeywords={ship detection, CUDA, polarimetric whitening filter, polarimetric covariance difference matrix, polarimetric synthetic aperture radar}
}

% 定义中英文摘要和关键字
\begin{cabstract}
  合成孔径雷达(SAR)作为一种主动成像的遥感观测手段，可以通过收发电磁波波束来获取地物目标的极化散射信息，生成高分辨率的地物影像。
  目前SAR被广泛应用于海上目标检测与识别。为满足SAR系统对海上目标检测的高时效性要求，本文共实现了三种基于CPU+GPU异构架构的高效并行舰船
  目标检测方法，总结如下：

  1)对于极化SAR图像，以极化白化滤波器(PWF)方法为例，实现了多GPU协同的并行极化白化滤波器舰船检测算法。该方法
  使用滑动窗选取局部海杂波像素来计算自适应极化白化滤波器参数，通过该滤波器融合各个极化通道的散射信息，得到一幅相干斑抑制图像。对重构降斑图像应用
  CFAR检测器进行阈值分割，得到最终的检测结果。实验结果表明，基于GPU的并行PWF舰船检测算法有效，并在检测时间性能上获得了显著的提升，明显优于传统的
  CPU串行算法。

  2)对于单极化SAR图像，采用了混合对数正态分布来描述强度图像中的非负海杂波分布。首先采用滑动传选择局部海杂波像素，
  然后采用最大期望(EM)方法来估计混合对数正态分布中参数，得到分布后根据给定的虚警率采用牛顿迭代法计算CFAR检测器的分割阈值。
  我们将该算法中参数估计与阈值计算等可并行执行的部分分配到GPU上去并行执行。实验结果表明，相比于传统CPU串行执行方式，
  该并行方法在时间性能上获得了数十倍的提升。

  3)实现了基于GPU的极化协方差差异矩阵极化SAR图像舰船检测方法。该方法计算了图像中每个像元与其3x3邻域
  极化协方差矩阵的差值，由此得到极化协方差差异矩阵。为了充分利用极化协方差差异矩阵中含有的极化信息，在每个GPU线程中，
  我们提取了极化协方差差异矩阵的SPAN值与基座舰船高度(PSH)这个极化特征，对这两个特征应用阈值分割，得到最终检测结果。
  实验结果表明：相较于PWF方法，该方法对复杂海况的适应能力更强，算法在检测精度与时间、空间性能上都优于PWF方法。

\end{cabstract}

% 如果习惯关键字跟在摘要文字后面，可以用直接命令来设置，如下：
% \ckeywords{\TeX, \LaTeX, CJK, 模板, 论文}

\begin{eabstract}
  Synthetic aperture radar (SAR) system provides an all-weather remote sensing method 
  that can generate high-resolution ground object images under radar beam irradiation. 
  Now, it has been widely used in Marine target detection and classification.In order 
  to meet the requirement of high timeliness of SAR ship target detection, this paper
  proposes a method based on CPU+GPU heterogeneous architecture for SAR image ship target 
  detection.In this paper, three kinds of efficient target detection based on CPU+GPU heterogeneous
  architecture are realized, these are summarized as follows:

  1)For polarization SAR images, with polarization whitening filter (PWF) method as an example,
  this paper implements the GPU collaborative parallel polarization filter algorithm, the method 
  estimates the local sea clutter covariance matrix and combine the polarization scattering channel information to 
  get a pair of coherent spot suppression images. For the reconstruct image, CFAR detector was applied to get the 
  final detection results.The experimental results show that the method is effective and the detection 
  time is improved significantly, which is better than the traditional method
  CPU platform.

  2)For SAR images, the log-mixture gaussian model is used to describe the non-negative 
  sea clutter distribution in amplitude SAR images, and the maximum expectation (EM) 
  method is used to effectively estimate the sea clutter distribution parameters. 
  According to the given false alarm rate in advance, the CAFR detection threshold is 
  obtained by Newton iteration method.The experimental results of this method on NVIDIA
  TITAN V GPU show that compared with the traditional CPU platform, the detection
  efficiency of this method is improved by dozens of times

 3)A ship detection method based on polarization covariance difference matrix is implemented.  This method calculates the polarization covariance matrix 
  difference between each pixel and its surrounding 3x3 neighborhood. The polarization covariance difference matrix improves
  the ship-sea contrast in the local area.  In order to make full use of the polarization and intensity features 
  in the polarization covariance difference matrix, the Shannon entropy of the polarization covariance
  difference matrix is ​​calculated, and the threshold is used for segmentation to obtain the final detection result.  
  Experimental results show that, compared with the PWF method, the detection accuracy of this method has been effectively improved.

 
\end{eabstract}

% \ekeywords{\TeX, \LaTeX, CJK, template, thesis}
